A new look at Pompeiu Triangles

### 2023-10-18 mathPaper/pompeiuTriangles.tex
final

\section{Reference}
Andreescu, T., Gelca, R. and Saul, M., 2009. Mathematical olympiad challenges (Vol. 216). Boston, MA: Birkhäuser.
Bényi, Á. and Caşu, L., 2009. Pompeiu's Theorem Revisited. The College Mathematics Journal, 40(4), pp.252-258.
Weatherburn, Charles Ernest. Elementary Vector Analysis: With application to geometry and physics. Bell and Sons, 1926.
\end{document}

>>>>

Using Eq. (\ref{eq:centroid2}) and the equivalents for $\vec{BP}$ and $\vec{CP}$, after multiplication by $k_1$,$k_2$, and $k_3$ and summation, we obtain

\begin{equation}
k_1\vec{AP}+k_2\vec{BP}+k_3\vec{CP}=0
\label{eq:psum}
\end{equation}

However, $\vec{AP}=\vec{AO}+\vec{OP}$, $\vec{BP}=\vec{BO}+\vec{OP}$ and $\vec{CP}=\vec{CO}+\vec{OP}.$, where $O$ is the center of the circumcircle of $\Delta ABC$. Therefore, Eq. (\ref{eq:psum}) can be rewritten as

\begin{equation}
k_1\vec{AO}+k_2\vec{BO}+k_3\vec{CO}=-(k_1+k_2+k_3)\vec{OP}
\label{eq:psum2}
\end{equation}

Taking the dot product of Eq. (\ref{eq:psum2}) with itself, we obtain
\begin{equation}
\begin{split}
k_1^2 AO^2+k_2^2 BO^2 +k_3^2 CO^2+\\
2k_1k_2\vec{AO}\cdot\vec{BO}+2k_1k_3\vec{AO}\cdot\vec{CO}+2k_2k_3\vec{BO}\cdot\vec{CO}=\\
(k_1+k_2+k_3)^2 OP^2
\end{split}
\label{eq:psum3}
\end{equation}

However, $AO=BO=CO=R$, where $R$ is the radius of the circumcircle of $\Delta ABC$, and 
$\vec{AO}\cdot\vec{BO}=\vec{BO}\cdot\vec{CO}$=
$\vec{CO}\cdot\vec{AO}=$
$-\frac{1}{2}R^2$. Therefore, Eq. (\ref{eq:psum3}) can be rewritten as
\begin{equation}
OP^2=\frac{k_1^2+k_2^2+k_3^2}{(k_1+k_2+k_3)^2}R^2-\frac{k_1k_2+k_1k_3+k_2k_3}{(k_1+k_2+k_3)^2}R^2
\label{eq:psum4}
\end{equation}
or
\begin{equation}
    OP^2=\left(1-3\frac{k_1k_2+k_1k_3+k_2k_3}{(k_1+k_2+k_3)^2}\right) R^2
    \label{eq:psum5}
\end{equation}
Therefore if $S(P(PA,PB,PC))$ is constant, $\frac{k_1k_2+k_1k_3+k_2k_3}{(k_1+k_2+k_3)^2}$ is also constant. Consequently, $OP$ is constant.  This means that the locus of points $P$ with constant area is a circle centered at $O$ with radius $OP$.

\section{Reference}

Andreescu, T., Gelca, R. and Saul, M., 2009. Mathematical olympiad challenges (Vol. 216). Boston, MA: Birkhäuser.\\
Bényi, Á. and Caşu, L., 2009. Pompeiu's Theorem Revisited. The College Mathematics Journal, 40(4), pp.252-258.\\
Weatherburn, Charles Ernest. Elementary Vector Analysis: With application to geometry and physics. Bell and Sons, 1926.
\end{document}
